Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-09-28 paper.tex
more on modularity

            LONI, FastR, Taverna and Pegasus are other examples of workflow 
            engines that 
            use an XML interface to describe CLIs. LONI enables generation of 
            the XML-based module interface through its GUI. The module interface
            consists of details on \note{from website} module metadata (e.g.
            authors, package, version, name) and citation information, 
            command-line syntax, parameter and file types, dependencies and 
            output and error handling.

@@

            Pegasus is another workflow engine that uses an XML format to 
            define the CLI tools interface. The XML interfaces are typically 
            incorporated directly into the workflow DAX definition. However, a 
            separate multiline text-based 'Transformation Catalogue' file can
            be provided. Information encoded within the interfaces include
            tool identifier (typically namespace::version), the URL or filepath
            to the executable, site identifier of the executable's host, 
            executable type (e.g. installed or staged) and the profile. Pegasus
            can also execute containerized tools. For this, a container 
            identifier, image URL, site identifier of the image, and container
            profiles must also be defined.

            Some workflows do not require module interfaces, as is the case with
            Make. The pipeline is expressed in a makefile containing a set of 
            rules. Rules consist of three components: targets, dependencies and
            recipes. The target is the output (typically a file) of the 
            execution of a recipe and the dependencies are the input required to 
            produce the given target. Recipes are the shell commands that will
            generate the target from its dependencies. As makefiles are written
            entirely using shell commands, it is not necessarily to create 
            interfaces to the shell commands of the tools.

>>>>

            LONI, FastR, Taverna, Pegasus and Galaxy are other examples of 
            workflow engines that 
            use an XML interface to describe CLIs. LONI enables generation of 
            the XML-based module interface through its GUI. The module interface
            consists of details on \note{from website} module metadata (e.g.
            authors, package, version, name) and citation information, 
            command-line syntax, parameter and file types, dependencies and 
            output and error handling.

@@

            Pegasus is another workflow engine that uses an XML format to 
            define the CLI tools interface. The XML interfaces are typically 
            incorporated directly into the workflow DAX definition. However, a 
            separate multiline text-based 'Transformation Catalogue' file can
            be provided. Information encoded within the interfaces include
            tool identifier (typically namespace::version), the URL or filepath
            to the executable, site identifier of the executable's host, 
            executable type (e.g. installed or staged) and the profile. Pegasus
            can also execute containerized tools. For this, a container 
            identifier, image URL, site identifier of the image, and container
            profiles must also be defined \note{from website}.

            While Galaxy is primarily a GUI-based application, an XML tool
            configuration file is required to add the tool to the application.
            The tool wrappers schema is very rich allowing for many tool 
            features to be defined. Similarly to many other workflow engine tool
            wrapper, the configuration file contains details on the tool name, 
            type, id, versions, command and input and output specifications. It
            also enables the execution of containerized tools. Furthermore,
            Galaxy enables users to specific actions to be performed on the 
            output files once created and define test cases.

            While many worfklow engines use XML or JSON to describe their tools,
            others wrap their tools in an interface defined by a
            programming/scripting language. Nipype, Pydpiper and Toil all use
            Python to create their wrappers; PSOM wrappers are written in
            MATLAB/Octave; OpenMOLE uses Java/Scala; and Make interfaces are
            written in Shell Script.

            Nipype's wrapper, written in Python, can encapsulate CLIs, SPM, 
            MATLAB and Python scripts. Attributes and methods that can be 
            defined for all interfaces include InputSpec, OutputSpec and a 
            Python dictionary of all expected outputs. InputSpec and OutputSpec
            are two Nipype classes. The former defines the input parameters of 
            a command and the second defines the outputs that are possibly 
            generated by the command. For CLIs, it is necessary to define the
            command. Additionally, Nipype will start X virtual framebuffer 
            before executing a CLI, if specified. For SPM interfaces, the job 
            type and name must be specified. Interfaces to MATLAB require 
            definition of the run function, while Python interfaces require
            the definition of the \textit{\_run\_interface} function. \note{from
            website}.

            Pydpiper's tools can either be custom Python code or CLIs. The 
            \textit{PipelineStage} and \textit{CmdStage} are used to 
            encapsulate the tools. The \textit{CmdStage} class is specifically 
            used to interface with CLIs, and thus, accepts a parsed array of the
            command and its parameters as input. Atoms, typically used to wrap
            around MINC file-format related tools, inherit from the
            \textit{CmdStage} class, and require the input MINC file (string or
            file handler) to be provided. A output file can also be specifiec, 
            but it must be of the same format as the MINC file (string or file 
            handler). Additionally, it is possible to pass multiple optional 
            arguments to the Atom.

            Toil is another workflow engine that describes their tool interfaces
            in Python. The wrappers, also known as \textit{Jobs} enable users to
            interface with custom Python code or Dockerized \note{cite Docker} 
            CLIs. Interfaces can be constructed either by creating a class that
            inherits from the \textit{Job} class or through the use of a 
            built-in function that converts the user-defined function (UDF) to a 
            Toil \textit{Job}. To convert, all that is required is the UDF,
            however, the user may also choose to include details on memory, 
            number of cores and disk space required. For Dockerized tools, Toil
            provides a built-in function that accepts the tool name, working dir
            and parameters of the tool.

            PSOM's tool interfaces are known as \textit{Bricks}. \textit{Bricks}
            can interface with any MATLAB function or CLI. Bricks require the
            definition of input and output files, in addition to a structure of
            program options. A useful feature found in PSOM is the ability 
            to perform a "dry-run" of the Brick without executing the command.

            OpenMOLE has the ability to encapsulate UDF Scala tasks and CLI. 
            In the case of CLI tasks, it is also possible to containerize or 
            encapsulate with CARE \note{cite} to make it portable.

            The Make pipeline is expressed in a makefile containing a set of 
            rules (Tool interfaces). Rules consist of three components: targets, 
            dependencies and recipes. The target is the output (typically a 
            file) of the 
            execution of a recipe and the dependencies are the input required to 
            produce the given target. Recipes are the shell commands that will
            generate the target from its dependencies.
